Measuring cross correlation function line-profile variations in radial-velocity measurements via a Skew Normal distribution

### 2018-04-10 manuscript_update.tex
Add files via upload
manuscript updated: new methodology (to be finished)

@@

Considering a random variable $Y\in \mathbb R$ (where $\mathbb R$ is the real line) which follows a SN distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density at some value $Y = y$ can be written as 
\begin{equation} \label{def:snd_gen}
SN(y;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\frac{\alpha(y-\xi)}{\omega}\right)
\end{equation}
where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a \emph{standard} normal distribution\footnote{A standard normal distribution is a normal distribution with a mean of 0 and a standard deviation of 1.}
 and $\alpha \in \mathbb R$ is the skewness parameter which quantifies the asymmetry of the SN.  We then write $Y \sim SN(\xi, \omega^{2}, \alpha)$ to mean that the random variable $Y$ follows the noted SN distribution.
Examples of SN densities under different skewness parameter values and the same location and scale parameters ($\xi = 0$ and $\omega = 1$) are displayed in Figure \ref{fig:SN.plot}.  A usual normal distribution is the special case of the SN distribution when the skewness parameter, $\alpha$, is equal to 0.\footnote{This can be seen from Equation~\eqref{def:snd_gen}.  If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0)$; this is the the probability a standard normal random variable is less than or equal to 0, which is $0.5$.  The $0.5$ cancels with the $2$ in the denominator and what remains is the usual normal density, $\frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$}
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 3in]{Skew_normal_densities_jjck.pdf} 
   \caption{Density function of a random variable $Y \sim SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$, and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
Note that the solid black line has an $\alpha = 0$ making it a normal distribution.   
   }
   \label{fig:SN.plot}
\end{figure}

@@

By using Eq. \ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution. For the $\alpha$ values used in Figure~\ref{fig:SN.plot}, the corresponding values of $\mu$, $\sigma^2$, $\gamma$ are displayed in Table~\ref{tab:cp_values}.  In particular, $\mu$ and $\sigma^2$ are the actual mean and the variance of the distribution (rather than simply a location and scale parameter), and $\gamma$ becomes an index for evaluating the asymmetry of the SN.  
%% Requires the booktabs if the memoir class is not being used
\begin{table}[htbp]
   \centering
   %\topcaption{Table captions are better up top} % requires the topcapt package
   \begin{tabular}{|cccc|} % Column formatting, @{} suppresses leading/trailing space
\hline
$\alpha$ & $\mu$ & $\sigma^2$ & $\gamma$ \\
\hline
 -3 	&	 -0.757	&	 0.427	&	 -0.667 \\
0	&	 0.000 	&	1.000	&	 0.000 \\
2	&	 0.714	&	 0.491	&	 0.454\\
6	&	 0.787	&	 0.381	&	 0.891\\
10	&	 0.794	&	 0.370	&	 0.956\\
\hline
   \end{tabular}
   \caption{CP values, $(\mu, \sigma^2, \gamma)$, corresponding to the $\alpha$ values from Figure~\ref{fig:SN.plot} (with location parameter $\xi = 0$ and scale parameter $\omega = 1$) using Equation~\eqref{eq:snd_cp}.  Values are rounded to three decimal places.}
   \label{tab:cp_values}
\end{table}
%
Further details about the parametrization from Equation~\eqref{def:snd_gen} (called the \emph{Direct Parametrization}), the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.

@@

Since each point of the CCF has a measurement error, this information is included in the specification of the SN distribution by introducing the following heteroskedastic function for the variance,
%
\begin{equation}
\text{var}(Y_{i})=\sigma^{2}+\sigma_{i}^{2}, \quad i = 1, \dots, n,
\label{eq:vaf}
\end{equation}
%
where $\sigma_{i}$ represents the measurement error for each point of the CCF. By using Eq. \ref{eq:vaf} we can interpret the parameter $\sigma^{2}$ \jessi{this is going to be confusing given the CP parametrization of the SN - one needs to be changes} as a measure of the pure variability present in the evaluation of the CCF. 
However, although useful for estimating correct error bars in the case where the different $\sigma_{i}$ do not include all systematics, this heteroskedastic function only considers Gaussian distributed residuals. \jessi{the previous statement is unclear}
%

The CCF is the result of a cross correlation so the residuals of a Normal or a SN fit are expected to show correlated noise.
To investigate this issue, we considered example CCFs from the star Tau Ceti.  The CCFs were modeled using a normal or a SN shape, and assuming independent normally-distributed noise around the modeled shape. 
%
We then subtracted the median of the residuals (the original data minus the fit function) obtained for all CCFs before performing a second round of fitting. The result of this procedure is illustrated in Figure~\ref{fig:Residual.comparison}. The lower left panel displays the residuals of a simple fit of a normal or a SN distribution, which appear to be strongly correlated. 
%
After removing the median of the residuals, in the lower right panel, the final residuals of the SN procedure have almost no apparent correlation, while the final residuals of the Normal procedure still present a small systematic component. This seems to be due to the asymmetric nature of the CCF (see Section~\ref{intro}), which is not captured in a symmetric distribution like the normal distribution.  This exercise highlights that the SN density shape better captures the shape of a CCF compared to a normal density shape.
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{[1]Plot_Fitting_and_Residuals_2run.pdf} 
   \caption{Comparison between the Normal and the SN procedures for modeling a collection of CCFs for the star Tau Ceti.  Two stages of modeling are carried out with the first stage results displayed in the left column and the second stage in the right column.
   The first run corresponds to fitting a normal or a SN shape to the raw CCF. The second run corresponds to fitting the same shape to the CCF after removing the median of all the residuals obtained in the first run. The SN residuals of the second run present minimal correlations, whereas the normal residuals present still a clear systematic component.}
   \label{fig:Residual.comparison}
\end{figure*}
%When using the least squares estimate for fitting the CCF with the SN distribution, we have to take into account the stationary problem in $\gamma=0$ due to the presence of the function $sign(\gamma)$ in Equation (\ref{eq:2}). Depending on the initial values of the numerical minimization for the least squares estimate of $\gamma$, the presence of this stationary point when evaluating $\gamma$ can lead to an incorrect estimation of the asymmetry parameter of the SN. In order to resolve this problem, we implemented two functions for retrieving the best least squares solution. In the first function we allowed for only positive solutions of $\gamma_1$ (with an upper limit of $0.995$), while in the second function only negative solutions are allowed (with a lower limit of $\gamma= -0.995$). The chosen solution is the estimate which has smallest residuals.

In the following of the paper, we define the RV as the mean of the normal or the mean of the SN (defined as SN RV). For the width of the CCF, we use the FWHM of the Normal, which is $2\sqrt(2\ln2)\sigma$. The width of the SN, SN FWHM, is defined in the same way\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the Normal case.}. In the Normal case, there is not an asymmetric parameter so we use BIS SPAN. This will be compared to the asymmetric parameter $\gamma_1$ of the SN. \jessi{Why use FWHM at all?  Why not just use the standard deviation since the FWHM just includes a multiplicative factor that is the same for all of them.}

@@

To correct for stellar activity signals, it is common to consider a linear combination of the RVs with the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case):
\comment{Is this really common? I am not aware of it having wide use in the community. If so, references would support this. The authors have to distinguish what their research group and collaborators do from what the rest of the community does.}
%
\begin{equation}
RV= \beta_{0} + \beta_{1}  \gamma + \beta_{2} FWHM + \epsilon,
\label{eq:RV:correction}
\end{equation}
%
where $\beta_{0}$ is the intercept and $\epsilon$ is the vector of the errors with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ is the identity matrix). 
\comment{Is this expression just for the RV from activity alone, or the measured RV from the star (contribution of all phenomena)? If it is just activity, you should put a subscript otherwise the readers will be confused. In the text you refer to the variable ?1, but Eq. 9 has no subscript in ?. You give one equation for Normal and SN, but in the text you state these variables have to be replaced by such and such when using SN, etc. It will be less confusing if you simply have two equations, one for Normal and one for SN and with their respective variables.}
When the Normal fit is used, the parameter $\gamma_1$ is replaced by the BIS SPAN and SN FWHM by FWHM. In order to show the goodness of this correction, a statistical test on the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ is presented, where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,1,2$. \jessi{the estimated values and p-values of the $\beta$'s does \underline{not} show goodness of fit.}
The level for not rejecting the null hypothesis is fixed equal to $0.05$. Pearson correlation coefficient $R^{2}$ is considered for explaining how well this linear combination explains the variability of the RVs of the star due to stellar activity. \jessi{$R^2$ is the coefficient of determination, and this should be explained better because it is not commonly used in astronomy as an assessment of the amount of variability explained by the model.}

@@

Alpha Centauri B $1816$ CCFs in 2010 are considered. Several measurement in 2010 are contaminated by light from Alpha Centauri A. To remove contaminated spectra and thus CCFs, we performed the same selection as presented in \citet{Dumusque-2012}.

We begin by evaluating the correlation between $\gamma$ and the BIS SPAN. In Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.933$ and a strong Pearson correlation coefficient of $0.958$. \jessi{It would be good to explain why you care about this.}
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 3in]{HD12862_[2]gamma_vs_bisspan.pdf} 
   \caption{Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.}
   \label{fig:alphacent:corr.gamma}
\end{figure}

@@

We show the correction of stellar activity using Eq. \ref{eq:RV:correction} in Fig.~\ref{fig:alphacent:correctionRV}. We see that after correcting for stellar activity, the rms of the RV residuals in the Normal and SN analysis are extremely similar. However, we note that when using the SN analysis, the correction is more important. This is confirmed by the statistical tests on the significance of the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ whose results are summarized in Table \ref{table:alfa:test}. The intercept and both the variables $\gamma$ and SN FWHM are necessary for correcting the RVs retrieved using a SN and Normal fitting. The comparison of $R^2$ shows as well that the SN case accounts for a higher percentage of  variability in RVs.

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{HD12862_[2]RadialVelocityDifferences.pdf} 
   \caption{RVs and RV differences for Alpha Centauri B considering a Normal and a SN fitting.}
   \label{fig:alphacent:diff:RV}
\end{figure*}

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{HD12862_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{RVs of Alpha Centauri B using a Normal and a SN fitting before and after correcting for stellar activity using Eq. \ref{eq:RV:correction}.
 \comment{Fig 5. The differences in the results of the two methods appear negligible to me}
   }
   \label{fig:alphacent:correctionRV}
\end{figure*}

\begin{table}[!t]
\begin{tabular}{|c|c|c|}
\hline
Parameter          & Normal Fitting         &   Skew Normal Fitting \\
\hline
$\beta_{0}$            &    $0.0066$    & $2.29e-11$ \\
\hline
$\beta_{1}$            &    $0.022$    & $2.22e-16$ \\
\hline
$\beta_{2}$            &     $2.22e-16$   &  $ 2.22e-16 $ \\
\hline
$R^{2}$      &     $0.49$    &  $0.77$   \\
\hline
\end{tabular}
\caption{\textbf{Alpha Centauri B}: Evaluation of the linear combination used for correcting the RVs from stellar activity, according to Eq. \ref{eq:RV:correction}. The p-values for the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ for both the methodologies are summarized, as well as the $R^2$. Although more significant for the SN, all parameters are useful in explaining the variability of the RVs of the star. The evaluation of the $R^2$ shows how the linear combination better explains the variability in RVs due to stellar activity coming from the SN analysis.}
\label{table:alfa:test}
\end{table}

We compare the correlation between the different activity indicators and the RVs of the star in Fig.~\ref{fig:alphacent:corrPlot}. The correlation between $\gamma_1$ and RVs is much stronger, almost twice, than the correlation calculated between the other asymmetry parameters and their corresponding RVs. The correlation between FWHM and the RVs is as well stronger when fitting a SN distribution. All the correlations are statistically different from $0$.

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{HD12862_[4]Comparison_para.pdf}  
   \caption{Correlation between the asymmetry parameters and the RVs for Alpha Centauri B. The last two plots show the correlation between the FWHM and the RVs for Alpha Centauri B using respectively the SN and the Normal fits.}
   \label{fig:alphacent:corrPlot}
\end{figure*}

%By looking closer to the data in Fig.~\ref{fig:alphacent:clusters}, we saw that there are three distinct temporal clusters in the Alpha Centauri B measurements and those clusters have a different linear relationship between $\gamma_1$ and RVs (and also SN FWHM and RVs, though not displayed here). When considering Eq. \ref{eq:RV:correction} and the subsequent inferences, this clustering is not accounted for in the model. A slightly more general linear model that allows for different intercepts and different slopes for the three clusters for $\gamma_1$ and SN FWHM can be considered.  Adjusting the RVs for stellar activity using this expanded model produces the corrected radial velocities displayed in the left plot of Fig.~\ref{fig:alphacent:clusters_residuals}.  Those corrected RVs are different from those displayed in the lower left plot of Fig.~\ref{fig:alphacent:correctionRV} (which apply the correction derived from Eq. \ref{eq:RV:correction}); the right plot of Fig.~\ref{fig:alphacent:clusters_residuals} displays the difference between the two sets of corrected RVs. The long-term trend can be explained by the fact that the RV drift induced by the companion Alpha Centauri A is not well corrected, however the shorter-term variations show that stellar activity varies as a function of time, with spots and faculae evolving, and therefore modifies the dependence of the RVs with respect to $\gamma_1$ and SN FWHM. These temporal variations is something that we want to explore more, however this work presents a significant effort that we want to address in a future paper.

%\begin{figure*}[htbp]
%   \centering
%\includegraphics[width = 6in]{AlphaCenB_clusters.pdf}  
%   \caption{The RVs as a function of time (left) and the RVs plotted against $\gamma_1$ (right) with colors and plot symbol according to its temporal cluster assignment for Alpha Centauri B. The RVs are expressed in \ms.}
%   \label{fig:alphacent:clusters}
%\end{figure*}
%\begin{figure*}[htbp]
%   \centering
%\includegraphics[width = 6in]{AlphaCenB_clusters_residuals.pdf}  
%   \caption{The RV for Alpha Centauri B corrected for stellar activity using the SN fit and accounting for the temporal clusters (left), and the difference between those values on in the left plot and the analogous values without accounting for the temporal clusters (right) which are displayed in the lower left plot of Figure~\ref{fig:alphacent:correctionRV}. The RVs are expressed in \ms.}
%   \label{fig:alphacent:clusters_residuals}
%\end{figure*}

@@

Thus, the RVs measured by the SN do not have the same precision than the RVs calculated using the Normal. This can be explained by the fact that in the case of the SN, variations in the asymmetry parameter $\gamma_1$ induce variations in the SN RV measured due to the strong correlation between those two parameters. Therefore, the errors in $\gamma_1$ propagate to the error in the SN RVs.
\comment{This seems to be the case in all your stars. I do not consider a method that delivers errors that are 60\% larger to be a very effective method.}
Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal or the SN are equivalent to 2.35$\times$\emph{noise}. Therefore, the precision in CCF width is the same if we fit a Normal or a SN to the CCF.

>>>>

\umberto{We considered CCFs having SNR larger than 10.}

@@

Considering a random variable $Y\in \mathbb R$ (where $\mathbb R$ is the real line) which follows a SN distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density at some value $Y = y$ can be written as 
\begin{equation} \label{def:snd_gen}
SN(y;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\frac{\alpha(y-\xi)}{\omega}\right)
\end{equation}
where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a \emph{standard} normal distribution\footnote{A standard normal distribution is a normal distribution with a mean of 0 and a standard deviation of 1.}
 and $\alpha \in \mathbb R$ is the skewness parameter which quantifies the asymmetry of the SN.  We then write $Y \sim SN(\xi, \omega^{2}, \alpha)$ to mean that the random variable $Y$ follows the noted SN distribution.
Examples of SN densities under different skewness parameter values and the same location and scale parameters ($\xi = 0$ and $\omega = 1$) are displayed in Figure \ref{fig:SN.plot}.  A usual normal distribution is the special case of the SN distribution when the skewness parameter, $\alpha$, is equal to 0.\footnote{This can be seen from Equation~\eqref{def:snd_gen}.  If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0)$; this is the the probability a standard normal random variable is less than or equal to 0, which is $0.5$.  The $0.5$ cancels with the $2$ in the denominator and what remains is the usual normal density, $\frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$}
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 4in]{Skew_normal_densities_jjck.pdf} 
   \caption{Density function of a random variable $Y \sim SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$, and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
Note that the solid black line has an $\alpha = 0$ making it a normal distribution.   
   }
   \label{fig:SN.plot}
\end{figure}

@@

By using Eq. \ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution. For the $\alpha$ values used in Figure~\ref{fig:SN.plot}, the corresponding values of $\mu$, $\sigma^2$, $\gamma$ are displayed in Table~\ref{tab:cp_values}.  In particular, $\mu$ and $\sigma^2$ are the actual mean and the variance of the distribution (rather than simply a location and scale parameter), and $\gamma$ becomes an index for evaluating the asymmetry of the SN. Beyond the mean of the SN, it is convenient to introduce a second location parameter that will be used in the analyses: the median. The median of the SN is defined as that value $m$ such that 
%
\begin{equation} \label{eq:snmed}
\int_{-\infty}^{m} SN(y;\xi, \omega, \alpha) = \frac{1}{2},
\end{equation}
%
where $SN(y;\xi, \omega, \alpha)$ follows Equation \ref{def:snd_gen}.\footnote{We recall that when using a symmetric distribution such as the Normal distribution, the mean and the median are equivalent.}

%% Requires the booktabs if the memoir class is not being used
\begin{table}[htbp]
   \centering
   %\topcaption{Table captions are better up top} % requires the topcapt package
   \begin{tabular}{|cccc|} % Column formatting, @{} suppresses leading/trailing space
\hline
$\alpha$ & $\mu$ & $\sigma^2$ & $\gamma$ \\
\hline
 -3 	&	 -0.757	&	 0.427	&	 -0.667 \\
0	&	 0.000 	&	1.000	&	 0.000 \\
2	&	 0.714	&	 0.491	&	 0.454\\
6	&	 0.787	&	 0.381	&	 0.891\\
10	&	 0.794	&	 0.370	&	 0.956\\
\hline
   \end{tabular}
   \caption{CP values, $(\mu, \sigma^2, \gamma)$, corresponding to the $\alpha$ values from Figure~\ref{fig:SN.plot} (with location parameter $\xi = 0$ and scale parameter $\omega = 1$) using Equation~\eqref{eq:snd_cp}.  Values are rounded to three decimal places.}
   \label{tab:cp_values}
\end{table}
%
Further details about the parametrization from Equation~\eqref{def:snd_gen} (called the \emph{Direct Parametrization}), the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.

@@

\umberto{Insert here a comparison of the N residuals and SN residuals?

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{[1]HD128621Residuals.pdf} 
   \caption{Comparison between the Normal and the SN procedures for modeling a collection of CCFs for the star Alpha Centauri b.}
    \label{fig:Residual.comparison}
\end{figure*}

}

%\umberto{here were discussed the implementation of the heteroskedastic function for the variance and the second run once removed the residuals median. Both these steps won't be in the new analyses.}
%%%%%% April 5th, 2018
%%% in the new Analyses both the heteroskedastic function for the variance and the second run are not considered
%%%%%%
\iffalse
Since each point of the CCF has a measurement error, this information is included in the specification of the SN distribution by introducing the following heteroskedastic function for the variance,
%
\begin{equation}
\text{var}(Y_{i})=\sigma^{2}+\sigma_{i}^{2}, \quad i = 1, \dots, n,
\label{eq:vaf}
\end{equation}
%
where $\sigma_{i}$ represents the measurement error for each point of the CCF. By using Eq. \ref{eq:vaf} we can interpret the parameter $\sigma^{2}$ \jessi{this is going to be confusing given the CP parametrization of the SN - one needs to be changes} as a measure of the pure variability present in the evaluation of the CCF. 
However, although useful for estimating correct error bars in the case where the different $\sigma_{i}$ do not include all systematics, this heteroskedastic function only considers Gaussian distributed residuals. \jessi{the previous statement is unclear}
%

The CCF is the result of a cross correlation so the residuals of a Normal or a SN fit are expected to show correlated noise.
To investigate this issue, we considered example CCFs from the star Tau Ceti.  The CCFs were modeled using a normal or a SN shape, and assuming independent normally-distributed noise around the modeled shape. 
%
We then subtracted the median of the residuals (the original data minus the fit function) obtained for all CCFs before performing a second round of fitting. The result of this procedure is illustrated in Figure~\ref{fig:Residual.comparison}. The lower left panel displays the residuals of a simple fit of a normal or a SN distribution, which appear to be strongly correlated. 
%
After removing the median of the residuals, in the lower right panel, the final residuals of the SN procedure have almost no apparent correlation, while the final residuals of the Normal procedure still present a small systematic component. This seems to be due to the asymmetric nature of the CCF (see Section~\ref{intro}), which is not captured in a symmetric distribution like the normal distribution.  This exercise highlights that the SN density shape better captures the shape of a CCF compared to a normal density shape.
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{[1]Plot_Fitting_and_Residuals_2run.pdf} 
   \caption{Comparison between the Normal and the SN procedures for modeling a collection of CCFs for the star Tau Ceti.  Two stages of modeling are carried out with the first stage results displayed in the left column and the second stage in the right column.
   The first run corresponds to fitting a normal or a SN shape to the raw CCF. The second run corresponds to fitting the same shape to the CCF after removing the median of all the residuals obtained in the first run. The SN residuals of the second run present minimal correlations, whereas the normal residuals present still a clear systematic component.}
   \label{fig:Residual.comparison}
\end{figure*}
%When using the least squares estimate for fitting the CCF with the SN distribution, we have to take into account the stationary problem in $\gamma=0$ due to the presence of the function $sign(\gamma)$ in Equation (\ref{eq:2}). Depending on the initial values of the numerical minimization for the least squares estimate of $\gamma$, the presence of this stationary point when evaluating $\gamma$ can lead to an incorrect estimation of the asymmetry parameter of the SN. In order to resolve this problem, we implemented two functions for retrieving the best least squares solution. In the first function we allowed for only positive solutions of $\gamma$ (with an upper limit of $0.995$), while in the second function only negative solutions are allowed (with a lower limit of $\gamma= -0.995$). The chosen solution is the estimate which has smallest residuals.
\fi
%%%%%%
%%%
%%%%%% April 5th, 2018

In the following of the paper, we define RV as the mean of the normal. Concerning the fit of the CCF using the SN, we present at first $2$ indicators that define the RV of the star: the mean of the SN, defined as SN mean RV and the median of the SN, defined as SN median RV. We will discuss the advantages of using this choice in the examples. For the width of the CCF, we use the FWHM of the Normal, which is $2\sqrt(2\ln2)\sigma$. The width of the SN, SN FWHM, is defined in the same way\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the Normal case.}. In the Normal case, there is not an asymmetric parameter so we use BIS SPAN. This will be compared to the asymmetric parameter $\gamma$ of the SN, called SN GAMMA. \jessi{Why use FWHM at all?  Why not just use the standard deviation since the FWHM just includes a multiplicative factor that is the same for all of them.}

@@

%\umberto{here the correction for stellar activity was discussed. In the new analyses we are using the median of the SN as indicator for RV of the star.}
%%%%%% April 5th, 2018
%%% in the new Analyses both the is no correction for stellar activity: the median of the SN is used
%%%%%%
\iffalse
To correct for stellar activity signals, it is common to consider a linear combination of the RVs with the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case):
\comment{Is this really common? I am not aware of it having wide use in the community. If so, references would support this. The authors have to distinguish what their research group and collaborators do from what the rest of the community does.}
%
\begin{equation}
RV= \beta_{0} + \beta_{1}  \gamma + \beta_{2} FWHM + \epsilon,
\label{eq:RV:correction}
\end{equation}
%
where $\beta_{0}$ is the intercept and $\epsilon$ is the vector of the errors with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ is the identity matrix). 
\comment{Is this expression just for the RV from activity alone, or the measured RV from the star (contribution of all phenomena)? If it is just activity, you should put a subscript otherwise the readers will be confused. In the text you refer to the variable ?1, but Eq. 9 has no subscript in ?. You give one equation for Normal and SN, but in the text you state these variables have to be replaced by such and such when using SN, etc. It will be less confusing if you simply have two equations, one for Normal and one for SN and with their respective variables.}
When the Normal fit is used, the parameter $\gamma$ is replaced by the BIS SPAN and SN FWHM by FWHM. In order to show the goodness of this correction, a statistical test on the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ is presented, where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,1,2$. \jessi{the estimated values and p-values of the $\beta$'s does \underline{not} show goodness of fit.}
The level for not rejecting the null hypothesis is fixed equal to $0.05$. Pearson correlation coefficient $R^{2}$ is considered for explaining how well this linear combination explains the variability of the RVs of the star due to stellar activity. \jessi{$R^2$ is the coefficient of determination, and this should be explained better because it is not commonly used in astronomy as an assessment of the amount of variability explained by the model.}
\fi
%%%%%%
%%%
%%%%%% April 5th, 2018

@@

A total of $1808$ CCFs measured in $2010$ have been analysed from the star Alpha Centauri B. Several measurement in 2010 are contaminated by light from Alpha Centauri A. To remove contaminated spectra and thus CCFs, we performed the same selection as presented in \citet{Dumusque-2012}.

We begin by evaluating the correlation between $\gamma$ and the BIS SPAN. In Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.99$ and a strong Pearson correlation coefficient of $0.96$. \jessi{It would be good to explain why you care about this.} This comparison is useful because $\gamma$ is an adimensional parameter taking information about the asymmetry of the SN while the BIS SPAN, beyond this, has got unit of measure of $km/s$. In other words, by using Fig.~\ref{fig:alphacent:corr.gamma}, it is possible to provide to $\gamma$ a physical meaning.
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 4in]{HD12862_[2]gamma_vs_bisspan.pdf} 
   \caption{Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.}
   \label{fig:alphacent:corr.gamma}
\end{figure}

@@

%%%%%%April 5th, 2018
%%% correction for stellar activity
%%%%%%
\iffalse
We show the correction of stellar activity using Eq. \ref{eq:RV:correction} in Fig.~\ref{fig:alphacent:correctionRV}. We see that after correcting for stellar activity, the rms of the RV residuals in the Normal and SN analysis are extremely similar. However, we note that when using the SN analysis, the correction is more important. This is confirmed by the statistical tests on the significance of the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ whose results are summarized in Table \ref{table:alfa:test}. The intercept and both the variables $\gamma$ and SN FWHM are necessary for correcting the RVs retrieved using a SN and Normal fitting. The comparison of $R^2$ shows as well that the SN case accounts for a higher percentage of  variability in RVs. 
\fi
%%%%%%
%%%
%%%%%% April 5th, 2018

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{HD12862_[2]RadialVelocityDifferences.pdf} 
   \caption{RVs and RV differences for Alpha Centauri B considering a Normal and a SN fitting.}
   \label{fig:alphacent:diff:RV}
\end{figure*}

%%%%%%April 5th, 2018
%%% correction for stellar activity
%%%%%%
\iffalse
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{HD12862_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{RVs of Alpha Centauri B using a Normal and a SN fitting before and after correcting for stellar activity using Eq. \ref{eq:RV:correction}.
 \comment{Fig 5. The differences in the results of the two methods appear negligible to me}
   }
   \label{fig:alphacent:correctionRV}
\end{figure*}

\begin{table}[!t]
\begin{tabular}{|c|c|c|}
\hline
Parameter          & Normal Fitting         &   Skew Normal Fitting \\
\hline
$\beta_{0}$            &    $0.0066$    & $2.29e-11$ \\
\hline
$\beta_{1}$            &    $0.022$    & $2.22e-16$ \\
\hline
$\beta_{2}$            &     $2.22e-16$   &  $ 2.22e-16 $ \\
\hline
$R^{2}$      &     $0.49$    &  $0.77$   \\
\hline
\end{tabular}
\caption{\textbf{Alpha Centauri B}: Evaluation of the linear combination used for correcting the RVs from stellar activity, according to Eq. \ref{eq:RV:correction}. The p-values for the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ for both the methodologies are summarized, as well as the $R^2$. Although more significant for the SN, all parameters are useful in explaining the variability of the RVs of the star. The evaluation of the $R^2$ shows how the linear combination better explains the variability in RVs due to stellar activity coming from the SN analysis.}
\label{table:alfa:test}
\end{table}
\fi
%%%%%%
%%%
%%%%%% April 5th, 2018

We compare the correlation between the different activity indicators and the RVs of the star in Fig.~\ref{fig:alphacent:corrPlot}. The correlation between $\gamma$ and RVs is much stronger, almost twice, than the correlation calculated between the other asymmetry parameters and their corresponding RVs. The correlation between FWHM and the RVs is as well stronger when fitting a SN distribution. All the correlations are statistically different from $0$.

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{HD12862_[4]Comparison_para.pdf}  
   \caption{Correlation between the asymmetry parameters and the RVs for Alpha Centauri B. The last two plots show the correlation between the FWHM and the RVs for Alpha Centauri B using respectively the SN and the Normal fits.}
   \label{fig:alphacent:corrPlot}
\end{figure*}

%By looking closer to the data in Fig.~\ref{fig:alphacent:clusters}, we saw that there are three distinct temporal clusters in the Alpha Centauri B measurements and those clusters have a different linear relationship between $\gamma$ and RVs (and also SN FWHM and RVs, though not displayed here). When considering Eq. \ref{eq:RV:correction} and the subsequent inferences, this clustering is not accounted for in the model. A slightly more general linear model that allows for different intercepts and different slopes for the three clusters for $\gamma$ and SN FWHM can be considered.  Adjusting the RVs for stellar activity using this expanded model produces the corrected radial velocities displayed in the left plot of Fig.~\ref{fig:alphacent:clusters_residuals}.  Those corrected RVs are different from those displayed in the lower left plot of Fig.~\ref{fig:alphacent:correctionRV} (which apply the correction derived from Eq. \ref{eq:RV:correction}); the right plot of Fig.~\ref{fig:alphacent:clusters_residuals} displays the difference between the two sets of corrected RVs. The long-term trend can be explained by the fact that the RV drift induced by the companion Alpha Centauri A is not well corrected, however the shorter-term variations show that stellar activity varies as a function of time, with spots and faculae evolving, and therefore modifies the dependence of the RVs with respect to $\gamma$ and SN FWHM. These temporal variations is something that we want to explore more, however this work presents a significant effort that we want to address in a future paper.

%\begin{figure*}[htbp]
%   \centering
%\includegraphics[width = 6in]{AlphaCenB_clusters.pdf}  
%   \caption{The RVs as a function of time (left) and the RVs plotted against $\gamma$ (right) with colors and plot symbol according to its temporal cluster assignment for Alpha Centauri B. The RVs are expressed in \ms.}
%   \label{fig:alphacent:clusters}
%\end{figure*}
%\begin{figure*}[htbp]
%   \centering
%\includegraphics[width = 6in]{AlphaCenB_clusters_residuals.pdf}  
%   \caption{The RV for Alpha Centauri B corrected for stellar activity using the SN fit and accounting for the temporal clusters (left), and the difference between those values on in the left plot and the analogous values without accounting for the temporal clusters (right) which are displayed in the lower left plot of Figure~\ref{fig:alphacent:correctionRV}. The RVs are expressed in \ms.}
%   \label{fig:alphacent:clusters_residuals}
%\end{figure*}

@@

Thus, the RVs measured by the SN do not have the same precision than the RVs calculated using the Normal. This can be explained by the fact that in the case of the SN, variations in the asymmetry parameter $\gamma$ induce variations in the SN RV measured due to the strong correlation between those two parameters. Therefore, the errors in $\gamma$ propagate to the error in the SN RVs.
\comment{This seems to be the case in all your stars. I do not consider a method that delivers errors that are 60\% larger to be a very effective method.}
Regarding the errors in width of the CCF, we see that the bootstrap analysis for the Normal or the SN are equivalent to 2.35$\times$\emph{noise}. Therefore, the precision in CCF width is the same if we fit a Normal or a SN to the CCF.
